A Survey of Range-Only SLAM Techniques and Sensors

### 2018-01-26 Paper.tex
Added Abstract and Part of Introduction

	\title{I am a title (RO SLAM Methods/Implementation Survey) }

	\author{David Grabowsky}

@@

	\begin{abstract}

		This is my abstract, there are many like it, but this one is mine. Will fill this in once paper is written ****

		An survey of current the current implementations and methodologies used for solving the range only systematic and localization problem (RO-SLAM).

	\end{abstract}

@@

@@

%	\includegraphics[width=90mm]{DNR.png}

@@

	\section{Beacon Initialization}
	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation. One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. Poorly approximated landmarks results in the divergence of the filter. These processes are furthur  divided into delayed and undelayed initializations.
	\subsection{Delayed initializations}
	These are the intialisations where  the robot intilaiialy moves around collects some measurements and initialises the location of the landmarks.This can be undersirable as it causes a delay in the localization of the robot where there is a immediate real time application. Localization can be performed only once a accurate estimations of the beacons are made. There are several methods that achieve this. 
	\subsubsection{Trilateration}
	[Pure Porbablisitc approach to SLAM] exmpalins a basic trilateration method where a basic 2D cicrcle intersectino technique. %more paperes needed
	\subsubsection{Particle filter}

	\cite{Caballero2010} presents a solution for this complication. A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.  This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden. \cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane. \cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation. The paper proposes that under different circumstances the landmark could be represented using different parameters. Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach. The results showed that when the circumstances can be clearly distinguished between, an increase in performance is seen.

@@

	\subsection{Fast SLAM}
	EKF is mainly used when we have a non-linear dynamic system model which has gaussian noise.[1]-[3].The quadratic complexity due to gaussian approximations of higher dimensions make the covariance matrix very large. This eventually cqauses higher complexity and leads to the divergence of the filter.The single data association problem also adds to this complexity. FastSLAM uses multiple hypothesis data association through particle filtering to overcome this problem. Thi allows it handle system models with non gaussians noise as well. This results in the computatoinal complexity to grow logarithmically instead of quadratic growth.

	FastSLAM utilizes the conditional Independence property of SLAM applications. If the path of the robot is known the correlation between the landmarks becomes zero. Hence in FastSLAM the robot path is initialised by using a particle fitler. Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in [Fast Slam paper 1]. Thus it maintains mutliple data hypothesis overcoming the EKF problem.

	$p(x^{k}_(1:t)$

>>>>

	\title{A Survey of Range-Only SLAM Techniques and Sensors}

	\author{David Grabowsky, Samyak Shetty, Sam Shue, James M. Conrad}

@@

	\begin{abstract}
		 A common aspect in many autonomous robotics applications is addressing the problem of Simultaneous Localization and Mapping (SLAM). In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, within the environment through sensors such as cameras and laser rangefinders. Sensing these landmarks provide the robot with information such as range and bearing, which are used in the estimation proses of the robot's pose and the landmark locations within the map. However, some applications use landmarks which are only capable of providing range information, such as wireless and acoutstic beacons. In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors (RO-SLAM) is explored. 	
	\end{abstract}

@@

	The Simultaneous Localization and Mapping (SLAM) problem is a common aspect of many autonomous robotics applications. SLAM involves estimating the pose of a mobile robot and building a map of its environment with no a priori information. The SLAM problem is a chicken-and-egg type problem, where the pose of the robot is with respect to a global frame, or map, and building a map requires knowledge of the robot's location. There are many algorithms used to solve this problem, most using a landmark-based approach. The concept of a landmark is identifying a distinguishable feature in the environment through camera or laser rangefinder and estimating the distance and orientation of that landmark relative to the robot. Then, as the robot traverses the environment, it can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map. In most SLAM applications, references to the map is synonymous with the locations of the landmarks.

	In outdoor SLAM applications, such as self-driving cars and autonomous farming equipment, global positioning satellite (GPS) readings are used in addition to the vehicle's odometry. While GPS has low resolution, it proves useful as it provides location information, which can help compensate for the accumulated error from drift in odometric sensors. However, GPS isn't available in all environments, such as indoors and underwater. Instead, wireless signals and sonar beacons are often used in indoors and underwater environments, respectively. While these beacons provide sensor information to the robotic vehicle, they don't inherently provide location information unless their positions are accurately known beforehand and are certain to never change. Wireless and sonar beacons are capable of providing range measurements instead.

@@

	\includegraphics[width=90mm]{DNR.png}

@@

	\section{Beacon Initialization}
	Beacons initialization refers to the process by which beacons (or landmarks) at an unknown position receive their initial position estimation. One of the complications with RO-SLAM involves the issue of determining the location of landmarks when their initial placement is unknown, the EKF, which is used by many implementations, is especially sensitive to poorly initialized landmarks as they are used as the basis for the convergence of an accurate estimate. \cite{Caballero2010} presents a solution for this complication. A Gaussian Mixture Model is integrated into the EKF to create a multiple hypothesis filter.  This multiple hypothesis approach is used to solve the RO-SLAM problem and its use allows for the un-delayed initialization of landmarks, however a large number of hypothesis can lead to increased computational burden. \cite{Geneve2015} also puts forward a method that utilizes a Gaussian mixtures for beacon initialization in EKF, but in this method only two hypotheses and a Cartesian plane. \cite{Ahmad2011a} proposes to reduce the computational burden of methods, such as the one proposed by \cite{Caballero2010}, by introducing a novel state vector that eliminates the need for multiple hypothesis landmark representation. The paper proposes that under different circumstances the landmark could be represented using different parameters. Four circumstances are presented in the paper and the method is tested in simulation using both the EKF and a least squares optimization approach. The results showed that when the circumstances can be clearly distinguished between, an increase in performance is seen.

@@

	\subsection{Fast SLAM}
